%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% WORK EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{rubric}{Work Experience}

\entry*[\role{Volunteer Community Organizer}]\company{Local Queer Mutual Aid Network} | 2024 -- Present

\emph{\relsize{-1}Community-building effort centered on recurring public events, community spaces, and mutual support.}


\achievement{Sustaining a 100+ member community network through recurring public events and community spaces, strengthening participation, trust, and mutual support.}

\achievement{Executing community events end-to-end: outreach, logistics, volunteer roles, \& accessibility planning.}

\vspace{0.5\baselineskip}

\entry*[\role{Founding Member \& Facilitator}]\company{Yes, Chef Mutual Aid Network} | 2025 -- Present

\emph{\relsize{-1}Coordinate weekly surplus community food distributions and volunteer operations.}


\achievement{Managing donation logistics, food preparation, and on-site operations for dozens of volunteers.}

\achievement{Maintaining consistent community communications supporting volunteer turnout and participation.}

\vspace{0.5\baselineskip}

\entry*[\role{Senior Business Operations Engineer}]\company{Mastercard} | 2023 -- 2025

\emph{\relsize{-1}Led operational performance reporting and service monitoring for global payment infrastructure across 40+ countries.}


\achievement{Built leadership dashboards integrating multiple data sources into unified reporting for stakeholders across 40+ countries; translated complex metrics into clear, accessible KPIs for decision-making.}

\achievement{Redesigned reporting workflows, reducing data delivery time from hours to seconds; documented processes enabling team self-service and sustainable operations.}

\achievement{Implemented data quality checks and reporting standards to ensure KPI accuracy and consistency across recurring stakeholder reports.}

\achievement{Created leadership-ready reporting narratives and documentation; mentored 3+ engineers in data storytelling and dashboard design standards.}

\achievement{Partnered with global teams to design monitoring and service disruption response workflows.}

\vspace{0.5\baselineskip}

\entry*[\role{Business Operations Engineer II}]\company{Mastercard} | 2022 -- 2023

\emph{\relsize{-1}Built reporting tools and automation to reduce manual work and improve operational consistency.}


\achievement{Developed automation for consistent, repeatable workflows to reduce manual operational toil.}

\achievement{Led documentation for \& onboarding of new team members for complex app ecosystem.}

\vspace{0.5\baselineskip}

\entry*[\role{Business Operations Engineer I}]\company{Mastercard} | 2021 -- 2022

\emph{\relsize{-1}Supported operational reporting and incident response for distributed systems.}


\achievement{Built alerts \& dashboards for real-time system health visibility and operational reporting.}

\achievement{Resolved 1,000+ production incidents annually for distributed payment systems.}

\vspace{0.5\baselineskip}

\entry*[\role{DevOps Assistantship}]\company{SIU Edwardsville / Illinois Department of Transportation} | 2020 -- 2021

\emph{\relsize{-1}Graduate assistantship supporting infrastructure and delivery workflows for public-sector systems.}


\achievement{Migrated critical public-sector infrastructure from Linux to Windows Server to gov't specifications.}

\vspace{0.5\baselineskip}

\entry*[\role{Founder \& Director}]\company{The Energy Illinois Project} | 2019 -- 2020

\emph{\relsize{-1}Designed a practicum-style program pairing engineering students with energy-industry mentors to deliver free energy audits \& efficiency plans for local businesses.}


\achievement{Designed program structure and workflows for student teams \& professional mentorship.}

\achievement{Presented program concept to professional engineer association; explored other funding pathways.}

\vspace{0.5\baselineskip}

\entry*[\role{Associate Consultant}]\company{SIU Applied Research Consultants} | 2019 -- 2020

\emph{\relsize{-1}Delivered end-to-end survey research and evaluation consulting for local and regional stakeholders.}


\achievement{Consulted end-to-end: Performed survey methodology \& public research for dozens of stakeholders.}

\achievement{Designed and executed survey projects: stakeholder intake, survey design, analysis, \& reporting.}

\achievement{Built R-based descriptive analysis \& visualization pipelines for reports using survey data.}

\achievement{Produced reports \& presentations translating findings into actionable recommendations.}

\vspace{0.5\baselineskip}

\entry*[\role{Volunteer Lab Associate}]\company{SIU Applied Research \& Neuroscience Labs} | 2018 -- 2020

\emph{\relsize{-1}Supported academic research through analysis tooling and automated processing workflows.}


\achievement{Built data workflows in Python \& R, accelerating analysis turnaround \& improving reproducibility.}

\end{rubric}