%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PROFESSIONAL EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{rubric}{Professional Experience}

\entry*[\role{Volunteer Community Organizer}]\company{Local LGBTQ+ Mutual Aid Network} | 2024 -- Present

\emph{\relsize{-1}Community-building effort centered on recurring public events, community spaces, \& mutual support.}


\achievement{Built \& sustained a 100+ member community network through recurring public events \& community spaces, strengthening participation, trust, \& mutual support.}

\achievement{Planned \& executed community events end-to-end: outreach, logistics, volunteer roles, accessibility planning, \& partner coordination.}

\vspace{0.5\baselineskip}

\entry*[\role{Founder \& Facilitator}]\company{Yes, Chef Mutual Aid Network} | 2025 -- Present

\emph{\relsize{-1}Coordinate weekly surplus community food distributions \& volunteer operations.}


\achievement{Coordinate weekly surplus food prep \& distribution serving hundreds of community members; manage donation logistics, volunteer scheduling, setup/teardown, \& on-site operations.}

\achievement{Maintain consistent community communications supporting volunteer turnout \& participation.}

\vspace{0.5\baselineskip}

\entry*[\role{Senior Site Reliability Engineer}]\company{Mastercard} | 2023 -- 2025

\emph{\relsize{-1}Senior SRE for global payment infrastructure processing billions in transactions annually across 40+ countries.}


\achievement{Architected \& deployed 200+ observability monitors across Splunk, Dynatrace, Domo, \& Omnibus, achieving 99.99\% uptime for critical payment systems.}

\achievement{Engineered monitoring-as-code framework with automated stage testing environments, enabling developers to validate alerts before production deployment.}

\achievement{Built secure Infrastructure-as-Code \& CI/CD pipelines using Chef, Jenkins, XLR, Bitbucket, \& Groovy, reducing deployment time throughout the delivery lifecycle.}

\achievement{Led comprehensive Domo operational intelligence platform integrating disparate data sources (Salesforce, Splunk, Dynatrace, Jira, Remedy) into live dashboards for ticket volume, remediation metrics, \& SLA performance across L2/L3 operations teams.}

\achievement{Rebuilt enterprise data pipelines in Domo; reduced report generation from 2+ hours to seconds while delivering SLO/SLI metrics \& BI capabilities for C-suite operations.}

\achievement{Built comprehensive monitoring documentation for Vocalink (Mastercard's account-to-account payment division) in Confluence with catalog of 200+ monitors, alerts, \& dashboards featuring self-updating dynamic tables for automated maintenance \& instant discoverability.}

\achievement{Led incident response as primary on-call engineer with <5min response SLA; conducted postmortems \& drove reliability improvements through SLO/SLI metric adoption.}

\achievement{Coached development teams on observability best practices, security-first engineering, \& infrastructure architecture; delivered monitoring documentation \& runbooks.}

\achievement{Built leadership dashboards integrating multiple data sources into unified reporting for stakeholders across 40+ countries; translated complex metrics into clear, accessible KPIs for decision-making.}

\achievement{Transformed operational data into clear narratives for leadership; created documentation \& training materials supporting cross-functional alignment.}

\achievement{Partnered with global teams to design outage response protocols, alert thresholds, \& response workflows.}

\vspace{0.5\baselineskip}

\entry*[\role{Site Reliability Engineer II}]\company{Mastercard} | 2022 -- 2023

\emph{\relsize{-1}Primary on-call SRE for MDES tokenization platform; maintained high availability through proactive monitoring, automated remediation, \& rapid incident response.}


\achievement{Engineered custom unified Python-based terminal platform for Tomcat monitoring, disk management, log rotation, \& service control with integrated API healthcheck capabilities; rolling dashboard accessible across all systems instead of rote commands on each host.}

\achievement{Built companion VSCode automation toolkit with pre-configured connection details, script hotkeys, direct Splunk/Dynatrace integration, \& database actions; greatly reduced release execution times \& emergency response delays through streamlined operational workflows.}

\achievement{Developed Python \& Bash automation scripts for deployment validation, health checks, \& compliance reporting, drastically reducing manual operational toil.}

\achievement{Led onboarding \& technical training for new SRE team members during platform expansion, delivering comprehensive instruction across 100+ microservices architectures, dozens of customer-specific call paths, \& complex multi-service transaction flows.}

\achievement{Applied PCI-DSS compliance automation implementations for payment systems.}

\achievement{Developed automation reducing manual operational work; created documentation supporting consistent, repeatable workflows across the team.}

\achievement{Built operational tools streamlining service disruption response; trained team members on processes that improved response consistency.}

\vspace{0.5\baselineskip}

\entry*[\role{Site Reliability Engineer I}]\company{Mastercard} | 2021 -- 2022

\emph{\relsize{-1}Supported operational reporting \& incident response for distributed payment systems.}


\achievement{Built observability dashboards in Splunk \& Dynatrace for real-time system health visibility.}

\achievement{Resolved 1,000+ L2/L3 production incidents annually for distributed payment systems.}

\achievement{Contributed to CI/CD pipeline enhancements including XLR \& Pivotal Cloud deployments.}

\vspace{0.5\baselineskip}

\entry*[\role{DevOps Assistantship}]\company{SIU Edwardsville / Illinois Department of Transportation} | 2020 -- 2021

\emph{\relsize{-1}Graduate assistantship supporting infrastructure \& delivery workflows for public-sector systems.}


\achievement{Migrated interactive traffic \& weather data website \& data pipeline from UNIX Apache to Windows Server IIS; rewrote site files in JavaScript, C++, Bash, \& HTML/CSS for the new environment.}

\achievement{Built \& configured Microsoft IIS server infrastructure for Illinois DOT public-facing applications.}

\vspace{0.5\baselineskip}

\entry*[\role{Founder \& Director}]\company{The Energy Illinois Project} | 2019 -- 2020

\emph{\relsize{-1}Designed a practicum-style program pairing engineering students with energy-industry mentors to deliver free energy audits \& efficiency plans for local businesses.}


\achievement{Designed program structure \& workflows for student teams \& professional mentors.}

\achievement{Presented program concept to a local Illinois professional engineers association.}

\vspace{0.5\baselineskip}

\entry*[\role{Associate Consultant}]\company{SIU Applied Research Consultants} | 2019 -- 2020

\emph{\relsize{-1}Delivered end-to-end survey research \& evaluation consulting for local \& regional stakeholders.}


\achievement{Designed \& executed end-to-end survey projects for multiple regional clients: stakeholder intake, survey design in Qualtrics \& SurveyMonkey, data analysis in R, Python, SQL, \& SPSS, \& final reporting.}

\achievement{Built R-based descriptive analysis \& visualization pipelines for reports including descriptive statistics, regression analyses, \& data visualizations.}

\achievement{Maintained long-term client relationships across Metro East \& Southern Illinois businesses \& university departments.}

\achievement{Built \& maintained entrance/exit surveys for the consultancy to develop curriculum \& ease transitions for incoming graduate students.}

\achievement{Maintained an interdisciplinary statistics education platform helping students across fields access data processing resources.}

\vspace{0.5\baselineskip}

\entry*[\role{Research Assistant}]\company{SIU Integrative Neuroscience Lab} | 2019 -- 2020

\emph{\relsize{-1}Implemented EEG data processing pipelines on supercomputing infrastructure \& supported academic research.}


\achievement{Implemented MatLab \& Octave EEG data processing pipelines to run in Linux environments on university supercomputers.}

\achievement{Configured 3D imaging software for construction of high-precision electroencephalographic head models.}

\achievement{Proofread \& corrected academic papers for publication.}

\vspace{0.5\baselineskip}

\entry*[\role{President}]\company{SIU Photogenesis} | 2018 -- 2019

\emph{\relsize{-1}Led university photography organization; grew membership \& revenue through client services, fundraising, \& event programming.}


\achievement{Grew organization membership from 5 to 40 members in a single semester through direct marketing \& outreach.}

\achievement{Increased organization funds from $2,000 to over $10,000 by implementing fundraising activities \& a new client photography revenue stream.}

\achievement{Oversaw publication of Lux, a nationally recognized fine art photography journal.}

\achievement{Designed new organizational branding, email newsletters, \& wrote a new constitution.}

\vspace{0.5\baselineskip}

\entry*[\role{Research Assistant}]\company{SIU Neurotrauma \& Rehabilitation Lab} | 2018 -- 2019

\emph{\relsize{-1}Conducted behavioral \& physiological research on animal models; performed statistical analyses.}


\achievement{Administered behavioral tasks \& physiological tests on animal models; managed care for research subjects.}

\achievement{Performed \& assisted in regression \& ANOVA analyses for multiple studies.}

\achievement{Analyzed golgi- \& immunofluorescent-stained tissue samples.}

\vspace{0.5\baselineskip}

\entry*[\role{Analog Process Technician}]\company{Southern Illinois University} | 2017 -- 2019

\emph{\relsize{-1}Operated \& maintained analog film processing equipment for university photography program.}


\achievement{Processed color film across multiple formats \& analog processes (C41, E6) using hand-operated JOBO processing equipment for all enrolled photography students.}

\vspace{0.5\baselineskip}

\entry*[\role{Research Intern}]\company{SIU Office of the Assistant Director of Retention} | 2016 -- 2017

\emph{\relsize{-1}Analyzed student enrollment \& retention data for university undergraduate admissions.}


\achievement{Performed detailed analysis on student enrollment \& retention data in R \& SPSS.}

\end{rubric}