%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{rubric}{Projects}

\achievement{\textbf{Proxmox Homelab} -- Terraform/Ansible IaC workflows \& GitLab CI/CD pipelines with separate production \& staging environments with physical isolation. Containerized with Docker Compose; networking using OPNsense.}

\githubproject{instant\_resume}{Automated LaTeX-based resume generation pipeline with YAML single source of truth, profile-based content filtering, \& Next.js web frontend with role-targeted views.}{https://github.com/aeholbrook/instant_resume}

\githubproject{net4nets (EEG Deep Learning Classification Pipeline)}{Convolutional neural net achieving 94\% accuracy classifying smokers from resting-state EEGs; end-to-end pipeline with time-frequency/PSD features \& CNN validation workflows.}{https://github.com/aeholbrook/net4nets}

\githubproject{sequence\_align}{NumPy-based protein sequence alignment algorithms with substitution matrix scoring.}{https://github.com/aeholbrook/sequence_align}

\githubproject{regression\_lesson\_jupyter}{Python tutorial explaining linear regression concepts with intuitive examples \& visual walk-throughs.}{https://github.com/aeholbrook/regression-lesson-jupyter}

\githubproject{2020 Commencement Report Pipeline}{R-based survey processing pipeline for consulting project; automated cleaning, aggregation, \& reporting outputs.}{https://github.com/aeholbrook/2020_commencement_report_pipeline}

\githubproject{aeholbrook.com}{Personal portfolio site built with Next.js; visual contact-sheet layout linking photography galleries, resume, \& project repos with custom typography \& scrollable storytelling.}{https://aeholbrook.com}

\githubproject{smalltown.gallery}{Interactive documentary photography platform showcasing small towns in Southern Illinois; searchable map interface with image galleries organized by town \& year. A project of the Department of Cinema \& Photography at SIU.}{https://smalltown.gallery}

\end{rubric}