%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PROFESSIONAL EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{rubric}{Professional Experience}

\entry*[\role{Volunteer Community Organizer}]\company{Local LGBTQ+ Mutual Aid Network} | 2024 -- Present

\emph{\relsize{-1}Community-building effort centered on recurring public events, community spaces, and mutual support.}


\achievement{Built and sustained a 100+ member community network through recurring public events and community spaces, strengthening participation, trust, and mutual support.}

\achievement{Planned and executed community events end-to-end: outreach, logistics, volunteer roles, accessibility planning, and partner coordination.}

\achievement{Synthesized community needs into actionable follow-ups, connecting individuals to resources and improving continuity across events.}

\vspace{0.5\baselineskip}

\entry*[\role{Founder and Facilitator}]\company{Yes, Chef Mutual Aid Network} | 2025 -- Present

\emph{\relsize{-1}Coordinate weekly surplus community food distributions and volunteer operations.}


\achievement{Coordinate weekly surplus food prep and distribution serving hundreds of community members; manage donation logistics, volunteer scheduling, setup/teardown, and on-site operations.}

\achievement{Maintain consistent community communications supporting volunteer turnout, reliability, and repeat participation.}

\vspace{0.5\baselineskip}

\entry*[\role{Senior Business Operations Engineer}]\company{Mastercard} | 2023 -- 2025

\emph{\relsize{-1}Led operational performance reporting and service monitoring for global payment infrastructure across 40+ countries.}


\achievement{Built leadership dashboards integrating multiple data sources into unified reporting for stakeholders across 40+ countries; translated complex metrics into clear, accessible KPIs for decision-making.}

\achievement{Redesigned reporting workflows, reducing data delivery time from hours to seconds; documented processes enabling team self-service and sustainable operations.}

\achievement{Transformed operational data into clear narratives for leadership; created documentation and training materials supporting cross-functional alignment.}

\achievement{Designed monitoring strategies and service disruption response protocols; partnered with global teams to set alert thresholds and response workflows.}

\vspace{0.5\baselineskip}

\entry*[\role{Business Operations Engineer II}]\company{Mastercard} | 2022 -- 2023

\emph{\relsize{-1}Built automation, reporting tools, and repeatable workflows supporting operational execution.}


\achievement{Developed automation reducing manual operational work; created documentation supporting consistent, repeatable workflows across the team.}

\achievement{Built operational tools streamlining service disruption response; trained team members on processes that improved response consistency.}

\achievement{Led onboarding and enablement for new team members across complex service ecosystems; delivered documentation supporting knowledge transfer.}

\vspace{0.5\baselineskip}

\entry*[\role{Business Operations Engineer I}]\company{Mastercard} | 2021 -- 2022

\emph{\relsize{-1}Supported operational reporting and incident response for distributed systems.}


\achievement{Built dashboards for real-time system health visibility and operational reporting; improved stakeholder visibility and data-driven decision-making.}

\achievement{Resolved 1,000+ production incidents annually for distributed payment systems; coordinated cross-functional troubleshooting and long-term fixes.}

\vspace{0.5\baselineskip}

\entry*[\role{DevOps Assistantship}]\company{SIU Edwardsville / Illinois Department of Transportation} | 2020 -- 2021

\emph{\relsize{-1}Graduate assistantship supporting infrastructure and delivery workflows for public-sector systems.}


\achievement{Migrated and recompiled critical public-sector infrastructure from Linux to Windows Server, improving operational compatibility and maintainability.}

\vspace{0.5\baselineskip}

\entry*[\role{Founder and Director}]\company{Energy Illinois} | 2019 -- 2020

\emph{\relsize{-1}Designed a practicum-style program pairing engineering students with professional engineers and energy-industry mentors to deliver no-cost energy audits and efficiency improvement plans for local businesses and nonprofits.}


\achievement{Designed program structure and workflows for student teams to deliver no-cost energy audits and efficiency recommendations with professional mentorship.}

\achievement{Presented program concept to the Illinois Professional Engineers Association; explored university funding pathways and external sponsorship options.}

\achievement{Created documentation including reporting templates and implementation planning; program paused March 2020 due to COVID-19 restrictions.}

\vspace{0.5\baselineskip}

\entry*[\role{Volunteer Lab Associate}]\company{SIU Applied Research \& Neuroscience Labs} | 2018 -- 2020

\emph{\relsize{-1}Supported academic research through analysis tooling and automated processing workflows.}


\achievement{Built automated data processing workflows in Python and R, accelerating analysis turnaround and improving reproducibility.}

\end{rubric}