%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EMPLOYMENT HISTORY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{rubric}{Employment History}

\entry*[2022 -- Present]\hspace{-0.3em}\role{Senior Software Engineer} \company{Tech Company Inc.}

\achievement{Lead development of core platform services supporting \textbf{millions} of users daily with 99.9\% uptime.}

\achievement{Built comprehensive monitoring and alerting system, reducing incident response time by \textbf{50\%}.}

\achievement{Designed and implemented microservices architecture using modern cloud technologies.}

\achievement{Mentored \textbf{3} junior engineers on software engineering best practices and system design.}

\vspace{0.5\baselineskip}

\entry*[2020 -- 2022]\hspace{-0.3em}\role{Software Engineer} \company{Tech Company Inc.}

\achievement{Developed and maintained RESTful APIs serving \textbf{10M+} requests daily with sub-100ms response times.}

\achievement{Implemented automated testing framework achieving \textbf{90\%+} code coverage.}

\achievement{Optimized database queries and caching strategies, improving performance by \textbf{40\%}.}

\vspace{0.5\baselineskip}

\entry*[2018 -- 2020]\hspace{-0.3em}\role{Junior Software Engineer} \company{Startup Solutions LLC}

\achievement{Built full-stack web applications using modern JavaScript frameworks and cloud services.}

\achievement{Developed user-facing features that increased customer satisfaction by \textbf{30\%}.}

\achievement{Implemented security best practices including authentication and data encryption.}

\vspace{0.5\baselineskip}

\entry*[Summer 2017]\hspace{-0.3em}\role{Software Development Intern} \company{Innovation Labs}

\achievement{Developed mobile application features using React Native for iOS and Android platforms.}

\achievement{Implemented data visualization dashboard for business intelligence and decision making.}

\end{rubric}